Best Practices for Developing Sustainable Scientific Software

### 2016-05-19 WSSSPE3/best_practices/main.tex

\author{Sandra Gesing$^{(1)}$,
Abani Patra$^{(2)}$,
Daniel S.\ Katz$^{(3)}$,
}

%
\thanks{{}$^{(1)}$ Center for Research Computing, University of Notre Dame, Notre Dame, IN, USA; sandra.gesing@nd.edu}
%
\thanks{{}$^{(2)}$ Mechanical and Aerospace Engineering, University at Buffalo, Buffalo, NY, USA; abani@buffalo.edu}
%
\thanks{{}$^{(3)}$ National Center for Supercomputing Applications (NCSA), Graduate School of Library and Information Science, and Electrical and Computer Engineering, University of Illinois, Urbana-Champaign, IL, USA; d.katz@ieee.org}
%

>>>>

\author{Sandra Gesing$^{(1)}$,
Abani Patra$^{(2)}$,
Daniel S.\ Katz$^{(3)}$,
Kyle E.\ Niemeyer$^{(4)}$,
Suresh Marru$^{(5)}$,
Dan Gunter$^{(6)}$
}

%
\thanks{{}$^{(1)}$ Center for Research Computing, University of Notre Dame, Notre Dame, IN, USA; sandra.gesing@nd.edu}
%
\thanks{{}$^{(2)}$ Mechanical and Aerospace Engineering, University at Buffalo, Buffalo, NY, USA; abani@buffalo.edu}
%
\thanks{{}$^{(3)}$ National Center for Supercomputing Applications (NCSA), Graduate School of Library and Information Science, and Electrical and Computer Engineering, University of Illinois, Urbana-Champaign, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(4)}$ School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(5)}$ Pervasive Technology Institute, Indiana University, USA; smarru@iu.edu}
%
\thanks{{}$^{(6)}$ Lawrence Berkeley National Laboratory, Berkeley, CA, USA; dkgunter@lbl.gov}
%
